Measuring Software Ticket Quality using Quantitative Data Analysis

### 2018-04-21 paper/paper.tex
Fix more issues inside the paper

Having discussed about various factors that can influence the quality in software tickets, 
we also need to take into account how can we apply this knowledge to solving the issue of 
poor design in issue tracking systems and how the ticket creation process could be improved. 
The study conducted by Lamkanfi et. al \cite{lamkanfi2010predicting} looks at this aspect and
shows how issue tracking systems could be extended in order to automatically generate the severity 
of a ticket (e.g. assign story points to a Jira issue). The authors conducted their research on the Mozilla,
GNOME and Eclipse and projects and split their approach into four steps:
  \begin{itemize}
    \item extract and organize tickets;
    \item pre-process tickets (i.e. tokenization, stop word removal and stemming);
    \item train the classifier on two datasets of tickets - 70\% 
      training and 30\% evaluation;
    \item apply the trained classifier on the evaluation set.
  \end{itemize}
The conclusions they drew from running the evaluation process were rather 
interesting:
  \begin{itemize}
    \item terms such as segfault, deadlock, crash, hand or memory typically indicate
      a severe bug;
    \item when analyzing the textual description they found that using simple
      one line summaries resulted in less false positives and increased precision
      levels;
    \item the classifier needs a large number of tickets in order to predict correctly;
    \item depending on how well a software project is modularised, one can 
      use a predictor per module rather than a universal one.
  \end{itemize}

@@

\section{Building the Data Set}\label{building}
The first step towards building the data set was to create a tool that was able to execute all the commands that we required:
fetching the tickets from any Jira instance, storing them into some form of database, analyze the variables of interest, 
automatically plot the correlations between them and run statistical analysis on the data. After careful consideration, 
we decided that Go was the best way to go for various reasons:
  \begin{itemize}
    \item it is designed with simplicity in min, thus making it easier for others who might join the project to read 
    and understand the codebase;
    \item it is compiled, statically typed, which implies that it is a much faster candidate than other interpreted languages
    such as Ruby or Python;
    \item is is designed with concurrency in mind, thus it helps reduce times of execution and computing power considerably;
  \end{itemize}

@@

Once the Bolt DB instance is completely populated with all the tickets we were interested in, the analyze command first 
fetches all the issues in the database. The next step is to filter out the tickets based on the following criteria:
\begin{itemize}
  \item tickets are \emph{High Priority} - the ticket status was marked either Blocker, Critical, Major or High;
  \item tickets were closed and had a maximum \emph{Time-To-Close} value of 27,000 hours (roughly 3 years) (we added the 
  higher bound as well in order to eliminate outliers produced by wrong data retrieved by Jira);
  \item remove outliers for all categories - some fields for a small number of tickets that had wrong values (e.g. one ticket
  had over 270,000 comments) introduced by the team behind the project and we needed to exclude them so that the analysis 
  produced correct results.
\end{itemize}

Then, it runs in parallel the \emph{seven types of analysis} for answering the research questions outlied in Section \ref{intro}, 
each in its own separate goroutine in order to speed up the process:
\begin{itemize}
  \item \emph{attachments} - checks whether attachments influence Time-To-Close and also look at what types 
  of attachments (e.g. screenshots, archive, code snippets) influence quality the most;
  \item \emph{steps to reproduce} - performs a complex regex to detect steps to reproduce and then checks whether their presence
  influence the quality of a ticket;
  \item \emph{stack traces} - runs complex regex for detecting exception stack traces in either summary, description or comments 
  and verifies whether their presence influence Time-To-Close for the ticket; this analysis only inspects projects
  written in Java as it is the most popular proponent built-in of stack traces;
  \item \emph{comments complexity} - loops through all comments and counts all words; then, the tool verifies whether 
  the number of words in comments has an impact on the Time-To-Close for the ticket;
  \item \emph{fields complexity} - same analysis as comments complexity, but only for summary and description wordiness;
  \item \emph{grammar correctness} - it uses Azure Cloud Bing Spell Check API \cite{bing} to perform analysis on summary, 
  description and comments; after concatenating everything and making it compatible with the API allowed formats, the tool 
  receives back in the JSON payload not only the number of flagged tokens (i.e. grammar errors), but also their types 
  (e.g. unknown token, misspell);
  \item \emph{sentiment} - uses Google Cloud Platform's Natural Language Processing API \cite{gcp_nlp} to retrieve the 
  sentiment score for summary, description and comments; it first concatenates everything and makes it conform to Google's 
  API and then sends the request, receiving a score from -1 to 1 inclusive (-1 means most negative, 1 means most 
  positive);
\end{itemize}

@@

The application first checks Bolt for tickets and gets either all of them in memory (easier to parse, 
but heavy on resource utilization) or slices them into smaller arrays to get processed afterwards (harder to parse as it 
eventually requires re-creation of the whole array of tickets before inserting back into the database, but it is much 
lighter on computing power). After having the tickets available, we start looping through them and perform all 
analysis types mentioned above. Once some sort of value is computed (e.g. grammar correctness score), it gets set in 
its corresponding field in the ticket struct and is subsequently stored back in the database. We chose this approach because 
we do not want to run the analysis every time we want to plot correlations between variables, but rather have the data 
already available there. Moreover, for analysis depending on third party services such as the Google Cloud Platform 
Natural Processing Language API, we would incur costs, thus having everything saved in the database and running the 
analysis only if the value has not been already computed allowed us to investigate the tickets without exceeding the 
free trial credits.

>>>>

Having discussed about various factors that can influence the quality in software tickets, 
we also need to take into account how can we apply this knowledge to solving the issue of 
poor design in issue tracking systems and how the ticket creation process could be improved. 
The study conducted by Lamkanfi et. al \cite{lamkanfi2010predicting} looks at this aspect and
shows how issue tracking systems could be extended in order to automatically generate the severity 
of a ticket (e.g. assign story points to a Jira issue). The authors conducted their research on the Mozilla,
GNOME and Eclipse and projects and split their approach into four steps: extract and organize tickets, 
pre-process tickets (i.e. tokenization, stop word removal and stemming), train the classifier on two datasets 
of tickets - 70\% training and 30\% evaluation and apply the trained classifier on the evaluation set.
The conclusions they drew from running the evaluation process were rather 
interesting:
  \begin{itemize}
    \item terms such as segfault, deadlock, crash, hand or memory typically indicate
      a severe bug;
    \item when analyzing the textual description they found that using simple
      one line summaries resulted in less false positives and increased precision
      levels;
    \item the classifier needs a large number of tickets in order to predict correctly;
    \item depending on how well a software project is modularised, one can 
      use a predictor per module rather than a universal one.
  \end{itemize}

@@

\section{Building the Data Set}\label{building}
The first step towards building the data set was to create a tool that was able to execute all the commands that we required:
fetching the tickets from any Jira instance, storing them into some form of database, analyze the variables of interest, 
automatically plot the correlations between them and run statistical analysis on the data. After careful consideration, 
we decided that Go was the best way to go for various reasons:
  \begin{itemize}
    \item it is designed with simplicity in mind, thus making it easy for others who might join the project to read 
    and understand the codebase; this would prove useful for us as developing the tool further is on our list of future 
    work items;
    \item it is a compiled, statically typed language that produces cross-platform executables when building the application;
    this is helpful for our research as we can use any machine or cluster of computers regardless of the operating system 
    running on them and collect even larger number of tickets than what we have collected so far;
    \item is is designed with concurrency in mind, thus it helps reduce times of execution and computing power considerably;
    in our case, why it helps us is by allowing access to goroutines, very lightweight threads that can scale even up to 
    millions; we use this powerful concept while fetching tickets from Jira or storing in the database - at one point, we had 
    more than 30,000 goroutines running at the same time.
  \end{itemize}

@@

Once the Bolt DB instance is completely populated with all the tickets we were interested in, the analyze command first 
fetches all the issues in the database. The next step is to filter out the tickets based on the following criteria:
\begin{itemize}
  \item tickets are \emph{High Priority} - the ticket status was marked either Blocker, Critical, Major or High;
  \item tickets were closed and had a maximum \emph{Time-To-Close} value of 27,000 hours (roughly 3 years) (we added the 
  higher bound as well in order to eliminate outliers retrieved by Jira);
  \item remove outliers for all categories - some fields for a small number of tickets that had extreme values (e.g. one ticket
  had over 270,000 comments) introduced by the team behind the project and we needed to exclude them so that the analysis 
  produced correct results.
\end{itemize}

Then, the analysis routine runs in parallel the \emph{seven types of analysis} for answering the research questions 
outlied in Section \ref{intro}, each in its own separate goroutine in order to speed up the process:
\begin{itemize}
  \item \emph{attachments} - checks whether attachments influence Time-To-Close and also look at what types 
  of attachments (e.g. screenshots, archive, code snippets) influence quality the most;
  \item \emph{steps to reproduce} - performs a complex regex to detect steps to reproduce and then checks whether their presence
  influence the quality of a ticket; the regular expression was adapted after the general guidelines elicited by 
  Bettenburg et. al \cite{bettenburg2008extracting} on how to extract structured data, including enumerations (of which 
  steps to reproduce are a subset);
  \item \emph{stack traces} - runs complex regex for detecting exception stack traces in either summary, description or comments 
  and verifies whether their presence influence Time-To-Close for the ticket; this analysis only inspects projects
  written in Java as it is the most popular proponent built-in of stack traces;
  \item \emph{comments complexity} - loops through all comments and counts all words; then, the tool verifies whether 
  the number of words in comments has an impact on the Time-To-Close for the ticket;
  \item \emph{fields complexity} - same analysis as comments complexity, but only for summary and description wordiness;
  \item \emph{grammar correctness} - it uses Azure Cloud Bing Spell Check API \cite{bing} to perform analysis on summary, 
  description and comments; after concatenating everything and making it compatible with the API allowed formats, the tool 
  receives back in the JSON payload not only the number of flagged tokens (i.e. grammar errors), but also their types 
  (e.g. unknown token, misspell);
  \item \emph{sentiment} - uses Google Cloud Platform's Natural Language Processing API \cite{gcp_nlp} to retrieve the 
  sentiment score for summary, description and comments; it first concatenates everything and makes it conform to Google's 
  API and then sends the request, receiving a score from -1 to 1 inclusive (-1 means most negative, 1 means most 
  positive);
\end{itemize}

@@

The application first checks Bolt for tickets and gets either all of them in memory (easier to parse, 
but heavy on resource utilization) or slices them into smaller arrays to get processed afterwards (harder to parse as it 
eventually requires re-creation of the whole array of tickets before inserting back into the database, but it is much 
lighter on computing power). After having the tickets available, we start looping through them and perform all 
analysis types mentioned above. Once a value is computed (e.g. grammar correctness score), it gets set in 
its corresponding field in the ticket struct and is subsequently stored back in the database. We chose this approach because 
we do not want to run the analysis every time we want to plot correlations between variables, but rather have the data 
already available there. Moreover, for analysis depending on third party services such as the Google Cloud Platform 
Natural Processing Language API, we would incur costs, thus having everything saved in the database and running the 
analysis only if the value has not been already computed allowed us to investigate the tickets without exceeding the 
free trial credits.
